---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# MittagLeffleR

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/MittagLeffleR)](https://cran.r-project.org/package=MittagLeffleR)
[![Downloads](http://cranlogs.r-pkg.org/badges/MittagLeffleR)](https://cran.r-project.org/package=MittagLeffleR)
[![DL_Total](http://cranlogs.r-pkg.org/badges/grand-total/MittagLeffleR?color=blue)](https://cran.r-project.org/package=MittagLeffleR)

The MittagLeffleR `R` package 

* calculates probability densities, probabilities and quantiles
* simulates random variables from both types Mittag-Leffler distributions
* fits a Mittag-Leffler distribution to data. 

The first type Mittag-Leffler distribution is a heavy-tailed distribution, 
and occurs mainly as a waiting time distribution in problems with
"fractional" time scales, e.g. times between earthquakes.

The second type Mittag-Leffler distribution is light-tailed, 
and "inverse" to the sum-stable distributions. 
It typically models the number of events in fractional systems and
is used for time-changes of stochastic processes, e.g. anomalous diffusion 
processes.


## Installation

You can install MittagLeffleR from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("strakaps/MittagLeffler")
```

## Examples

### Fitting a Mittag-Leffler distribution

Generate a dataset first:

```{r, echo=TRUE}
library(MittagLeffleR)
y = rml(n = 10000, tail = 0.9, scale = 2)
```

Fit the distribution: 

```{r}
logMomentEstimator(y, 0.95)
```

Read off 

* the shape parameter $0 < \nu < 1$, 
* the scale parameter $\delta > 0$, 
* their 95% confidence intervals. 

### Calculate the probability density of an anomalous diffusion process

Standard Brownian motion with drift $1$ has, at time $t$, 
has a normal probability density 
$n(x|\mu = t, \sigma^2 = t)$.
A fractional diffusion at time $t$ has the time-changed probability density 

$$p(x,t) = \int n(x| \mu = u, \sigma^2 = u)h(u,t) du$$

where $h(u,t)$ is a second type Mittag-Leffler probability density with 
scale $t^\alpha$. (We assume $t=1$.)

```{r CTRW-limit, warning=FALSE}
tail <- 0.65
dx <- 0.01
x <- seq(-2,5,dx)
umax <- qml(p = 0.99, tail = tail, scale = 1, second.type = TRUE)
u <- seq(0.01,umax,dx)
h <- dml(x = u, tail = tail, scale = 1, second.type = TRUE)
N <- outer(x,u,function(x,u){dnorm(x = x, mean = u, sd = sqrt(u))})
p <- N %*% h * dx
plot(x,p, type='l', main = "Fractional diffusion with drift at t=1")
```


### Vignettes

To display the vignettes, do `help(package="MittagLeffleR")` and 
click on the vignettes link. 

- **MLdist.Rmd:** shows plots with the basic properties of the two
              distributions.
- **probsNquantiles.Rmd:** details about how probability densities, quantiles
              and random variables are calculated using the Mittag-Leffler
              function and the package `stabledist`
- **parametrisation.Rmd:** details about how the parameters for the stable
              distribution were chosen. 

